---
title: "example_r_challenges"
output: html_document

--- type:MultipleChoiceChallenge key:167A4VcDii9Ku
## True basics

*** =assignment1
Which symbol marks the beginning of a comment in R?

*** =options1
- `%`
- `%*`
- [`#`]
- `@`
- `$`
- `*`
- `/*`


*** =assignment2
Which of the following is the recommended method of assigning a value to a variable?

*** =options2
- [`z <- 3`]
- `z is 3`
- `z gets 3`
- `z -> 3`
- `z == 3`


*** =assignment3
Which function is used to view the contents of your workspace?

*** =options3
- `show()`
- [`ls()`]
- `view()`
- `View()`
- `view_contents()`
- `show_workspace()`
- `view_workspace()`


--- type:OutputChallenge key:167oSz8A19yBt
## Identify the class of an object

*** =code
```{r}
x <- {{var1}}
class(x)
```

*** =variables
var1:
  - '-1.3'
  - 'c(5, 1)'
  - '"FALSE"'
  - '"TRUE"'
  - 'c(TRUE, FALSE)'
  - 'c("b", "a")'
  - 'c(FALSE, TRUE)'
  - 'TRUE'
  - 'FALSE'
  - 'c("-2", "3")'
  - 'c(12, -10)'

--- type:BlanksChallenge key:167y3A7MS2X70
## Create a vector

*** =code
```{r}
{{var1}} <- {{_fun1}}({{var2}})
{{var1}}
```

*** =variables
var1:
  - 'x'
  - 'y'
  - 'z'
var2:
  - '11, 8, 10, 15'
  - '12, 17, 5, 19'
  - '-8, -4, 2'
  - '-9, -10, -2'
  - 'FALSE, TRUE, TRUE'
  - 'TRUE, FALSE, TRUE'
  - '"January", "June", "December"'
  - '"May", "June", "March"'
  - '"December", "September", "February"'
fun1:
  - 'c'
